---
title: "Workshop preparations"
description: |
  Instructions on preparations to be made by learners before the workshop
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Recommended setup
This workshop is a combination of presentation and live coding.
If you are attending it as a webinar, having a dual monitor set-up is recommended. 
This would enable you to follow the live coding, by also typing in the commands and experience the effects your self.
Programming is a skill where you learn best by doing.

## Install R
Make sure to have R installed on your computer.
It is recommended that you have a newer version of R installed, preferably higher than 4.0.0, but at minimum higher than 3.5.3.
Download R from [the R-project](https://www.r-project.org/)

#### Windows computers
The tidyverse packages require [rtools](https://cran.r-project.org/bin/windows/Rtools/) to be installed. 
Make sure to have the required version installed before proceeding.

## Install RStudio

The best experience with the workshop is to have an RStudio newer than 1.3. 
It is not necessary, but highly recommended.

[RStudio downloads page](https://rstudio.com/products/rstudio/download/#download)

## Required packages

The course will use four packages, so please have these installed prior to the course beginning.

```{r, eval = FALSE}
install.packages(c("lme4", "tidyverse", "broom", "broom.mixed"))
```

If you are struggling to install the package, please create [a ticket](https://github.com/Athanasiamo/LME_introduction_workshop/issues) pasting the command and output you get so I can help you get it sorted.
